Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-31 paper_comparison/paper_comparison/paper_comparison.Rmd
update the same section

The "Butterfly" shape on the other hand seems to be

>>>>

The chance of detecting the "Butterfly" shape is roughly the same as the chance of detecting the "Left-triangle" shape in both tests. The only noticeable difference from Figure \ref{fig:heter-power-uniform-a} is the Breusch-Pagan test has slightly higher power for detecting this shape compared to other two shapes when the effect size is low.

### 2023-01-31 paper_comparison/paper_comparison/paper_comparison.tex
update heter shape section
update the same section

Shape of the non-linearity pattern is another factor contributes to the
non-linearity model. With different non-linearity patterns, it is
expected that the visual test will respond variously.

According to Figure \ref{fig:poly-power-uniform-j}, conventional tests
have almost identical power in testing the ``U'', the ``S'' and the
``M'' shape, except for testing the ``Triple-U'' shape, which have
significantly lower power. To understand why this is, one needs to
return to the way the RESET test is applied. It requires a parameter
indicating degree of fitted values to test for, and the recommendation
is to generically use four (\citet{ramsey_tests_1969}). However, the
``Triple-U'' shape constructed from the Hermite polynomials use power up
to 18. If the RESET test had been applied using a higher power no less
than six, the power curve of ``Triple-U'' shape will have little
difference to other shapes. The recommendation of the polynomial power
for the RESET should be revised, perhaps. This illustrates the
sensitivity of conventional testing to the parameters, and it also
points to a limitation that one needs to know the data structure in
order to set the parameters for the test.

For visual tests, we expect the ``U'' shape will be the easiest one to
be detected by subjects followed by the ``S'', ``M'' and ``Triple-U''
shape. From Figure \ref{fig:poly-power-uniform-j}, it can be observed
that the power curves are mostly aligned with our expectation, except
for the ``M'' shape. Interestingly, the ``M'' shape is as easy to be
detected as the ``U'' shape, which implies the readability of the shape
do not strictly follow the degree of the polynomials.

@@

>>>>

A primary factor contributes to the non-linearity model is the shape of
the non-linearity. According to Figure \ref{fig:poly-power-uniform-j},
conventional tests have almost identical power in testing the ``U'', the
``S'' and the ``M'' shape, except for testing the ``Triple-U'' shape,
which have significant lower power. To understand why this is, one needs
to return to the way the RESET test is applied. It requires a parameter
indicating degree of fitted values to test for, and the recommendation
is to generically use four (\citet{ramsey_tests_1969}). However, the
``Triple-U'' shape constructed from the Hermite polynomials use power up
to 18. If the RESET test had been applied using a higher power no less
than six, the power curve of ``Triple-U'' shape will have little
difference to other shapes. The recommendation of the polynomial power
for the RESET should be revised, perhaps. This illustrates the
sensitivity of conventional testing to the parameters, and it also
points to a limitation that one needs to know the data structure in
order to set the parameters for the test.

For visual tests, we expect the ``U'' shape will be the easiest one to
be detected by subjects followed by the ``S'', ``M'' and ``Triple-U''
shape. From Figure \ref{fig:poly-power-uniform-j}, it can be observed
that the power curves are mostly aligned with our expectation, except
for the ``M'' shape, which is as easy to be detected as the ``U'' shape.
This implies the readability of the shape do not strictly follow the
degree of the polynomials.

@@

We also investigate the impact of different heteroskedasticity shapes on
power of conventional tests and visual tests. In theory, the
``Left-triangle'' and the ``Right-triangle'' shapes are functionally
identical from the point of view of a Breusch-Pagan test. As shown in
Figure \ref{fig:heter-power-uniform-a}, this is indeed the case where
little difference between the power curves can be perceived. Similarly,
visual tests will have the same power of detecting these two shapes if
they are equally likely to be identified. However, it can be observed
from Figure \ref{fig:heter-power-uniform-a} that the power curve for the
``Left-triangle'' shape is constantly higher than the one for the
``Right-triangle'' shape, indicating a potential favour of orientation
by human, which is worth to be explored in future studies.

The chance of detecting the ``Butterfly'' shape is roughly the same as
the chance of detecting the ``Left-triangle'' shape in both tests. The
only noticeable difference from Figure \ref{fig:heter-power-uniform-a}
is the Breusch-Pagan test has slightly higher power for detecting this
shape compared to other two shapes when the effect size is low.

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/heter-power-uniform-a-1}

\caption{Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$.}\label{fig:heter-power-uniform-a}
\end{figure}
